---
title: "gtR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gtR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

You can install the package from [GitHub](https://github.com/shanej90/gtR) using the following code:

``` {r install, eval = F }
remotes::install_github("shanej90/gtR")
```

## How it works
`gtR` simplifies the process of accessing the UKRI Gateway to Research API.

Currently, it lets you:

* View a list of endpoints (`gtr_endpoints`).
* View a list of resource combinations used in certain functions (`gtr_combinations`).
* Get configuration details for said endpoints (`get_configs()`).
* Query the API using `get_resources()`. This allows to return all results for a given 'resource' (eg, project, organisation), or resources linked to a specific entity (eg, all projects for an organisation). It also let's you specify whether you want to return all pages or specific ones, or filter your results using search terms.
* There are also legacy functions that 'compartmentalise' the functionality offered by `get_resources()`. These allow you to check all results for a given resource `query_resource_all()` or those that are linked to a specific entity (`query_resource_combination()`). These legacy functions also provide the option to return metadata about your query instead of just the 'actual' results.


## Examples

__NB I won't show some actual data outputs as there are some hideously long ID strings in there__.

You want to try and identify the University of Exeter's record in the API.

```{r example_1, echo = T}

library(gtR)

data <- get_resources(resource = "organisation", page_nums = 1, size = 10)

```

You can't see Exeter in here. However, you're only looking at the first page. You could try and return more results per page, or try a different page, but doing this randomly wouldn't be very efficient. What if we try searching specifically for the term "Exeter"?

```{r example_2, echo = T}

#return configuration for organisation records to look up field codes to search against

org_config <- get_configs("organisation")

org_config$fields

#so we can see we need to search against "org.n" to look up the name.
#The configuration file shows this is searched anyway, so we don't need to reference the code, but will for completeness

final_result <- get_resources("organisation", size = 30, search_term = "Exeter", search_fields = "org.n")

```

Success (third row)!
