---
title: "Results related to a specific entity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gtR_combination}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

__Note this article relates to a legacy functions. Its capabilities are now covered by `get_resources()`.__

## Introduction

The `query_resource_all()` function enables you to retrieve all records for a particular resource using a search term. If you want to limit the records returned to a specific institution, this requires additional arguments.

`query_resource_combination()` uses a list of defined combinations of resources (`gtr_combinations`) as well as an `id` argument to refine the records and only include those that match your resource combination and `id`.

## Process

1. First you will need to check `gtr_combinations` to identify what resource combinations are required. The first resource in these combinations is what we will be filtering against using the `id` argument, and the second resource are the records that will be returned (eg. the "organisation project" combination will return all projects for a specific organisation, where the organisation is determined by the `id`).

2. Next you need to retrieve the `id` that will be used to filter the resource. This can be done by using the `query_resource_all` function and making note of the `id` of the relevant record.
 
3. You can now use `query_resource_combination` function with the two resources found in `gtr_combinations` and the `id` retrieved from `query_resource_all`.

## Example

You want to return all projects linked to the University of Exeter.

```{r example_1.1, echo = T}

library(gtR)

exeter_id <- query_resource_all(
  resource = "organisation",
  search_term = "Exeter"
  )

id <- "961756BF-E31F-4A13-836F-0A09BA02385C"

data <- query_resource_combination(
  resource = "organisation",
  output = "project",
  "961756BF-E31F-4A13-836F-0A09BA02385C",
  size = 10
)

data

```
